Translation of B Implementations to the LLVM: Specification

### 2014-04-01 DOCUMENTATION/DerivedTypes.tex
Removing C examples

\section{Translation of Structures and Array}

@@

\section{Arrays}

The arrays store a fixed-size sequential collection of elements with the same type. 
They consist of contiguous memory locations, where the lowest address (0) 
corresponds to the first element and the highest address to the last element.
In B, a concrete array is a total function where the domain indexes the range 
elements. Declaration examples of arrays are:
\begin{itemize}
	\item $array1 \in (0..10) \to INT $	(a simple array)
	\item $array2 \in (1..10) \times (1..20) \times (1..30) \to INT $   (a multidimensional array)
	\item $\{1\vdash1\vdash4, 1\vdash2\vdash5\}  \in (INT \times INT) \times INT$ (an initialised array)
\end{itemize}

\subsection{Relation arrays B0 and LLVM}

@@

The following blocks illustrate a C code setting a value to array
and its translation to LLVM.

\begin{ccode} 
int x=2; int y=3; int z=4;
Array2[x][y][z]=7;
\end{ccode}

This example is translated in four steps. First, the variables \%x, \%y, \%z 
are allocated. Second, the respective values 2, 3, 4 are stored in variables. 
Third, the variables are loaded to local variables and converted to 64 bits. 
Finally, the address of array is calculated in local variable \%7 and the value 
7 is stored in it.  
\begin{figure}[h]
\begin{llvmcode}
%x = alloca i32
%y = alloca i32
%z = alloca i32
store i32 2, i32* %x
store i32 3, i32* %y
store i32 4, i32* %z
%1 = load i32* %z
%2 = sext i32 %1 to i64
%3 = load i32* %y
%4 = sext i32 %3 to i64
%5 = load i32* %x
%6 = sext i32 %5 to i64
%7 = getelementptr[10x[20x[30xi32]]]*@Array2,i32 0,i64 %6,i64 %4,i64 %2;getting an element
store i32 7, i32* %7         ;setting an element
\end{llvmcode}
\end{figure}

>>>>

\section{Translation of Structures and Array}
\label{sec:StructArray}

@@

\subsection{Arrays}

The arrays store a fixed-size sequential collection of elements with the same type. 
They consist of contiguous memory locations, where the lowest address (0) 
corresponds to the first element and the highest address to the last element.
In B, a concrete array is a total function where the domain indexes the range 
elements. Declaration examples of arrays are:
\begin{itemize}
	\item $array1 \in (0..10) \to INT $	(a simple array)
	\item $array2 \in (1..10) \times (1..20) \times (1..30) \to INT $   (a multidimensional array)
	\item $\{1\mapsto1\mapsto4, 1\mapsto2\mapsto5\}  \in (INT \times INT) \times INT$ (an explicit array)
\end{itemize}

\subsubsection{Relation arrays B0 and LLVM}

@@

The following blocks illustrate a B code setting a value to array
and its translation to LLVM.

\begin{pascalcode} 
VAR xx, yy, zz IN
	xx=2;
	yy=3;
	zz=4;
	Array2(x,y,z):=7
END
\end{pascalcode}

This example is translated in four steps. First, the variables \%x, \%y, \%z 
are allocated. Second, the respective values 2, 3, 4 are stored in variables. 
Third, the variables are loaded to local variables and converted to 64 bits. 
Finally, the address of array is calculated in local variable \%7 and the value 
7 is stored in it.  
\begin{figure}[h]
\begin{llvmcode}
%xx = alloca i32
%yy = alloca i32
%zz = alloca i32
store i32 2, i32* %xx
store i32 3, i32* %yy
store i32 4, i32* %zz
%1 = load i32* %zz
%2 = sext i32 %1 to i64
%3 = load i32* %yy
%4 = sext i32 %3 to i64
%5 = load i32* %xx
%6 = sext i32 %5 to i64
%7 = getelementptr[10x[20x[30xi32]]]*@Array2,i32 0,i64 %6,i64 %4,i64 %2;getting an element
store i32 7, i32* %7         ;setting an element
\end{llvmcode}
\end{figure}
